---
title: "finalProjectDoc"
format: html
editor: visual
---

## Importing packages

```{r}
library(tidyverse)
library(dplyr)
library(lme4)
library(ggplot2)
```

### Importing data

data comes from the Kaggle Pizza Price Prediction dataset

<https://www.kaggle.com/datasets/knightbearr/pizza-price-prediction/data>

```{r}
pizza_data <- read_csv("~/classes/DS303_SP25/finalproj/pizza_v1.csv")

str(pizza_data)
```

quickly editing the data

```{r}
pizza_data <- pizza_data %>%
  mutate(price_rupiah = gsub("Rp|,", "", price_rupiah),  
         price_rupiah = as.numeric(price_rupiah)) 

pizza_data$size <- factor(pizza_data$size)
```

### Exploring the data

```{r}
ggplot(pizza_data, aes(x = diameter, y = price_rupiah)) +
  geom_point(alpha = 0.7) +
  labs(title = "Pizza Price vs Diameter", x = "Diameter (inches)", y = "Price (Rp)") +
  theme_minimal()

```

```{r}
ggplot(pizza_data, aes(x = size, y = price_rupiah)) +
  geom_boxplot(fill = "orange", alpha = 0.7) +
  labs(title = "Pizza Price by Size Category", x = "Size", y = "Price (Rp)") +
  theme_minimal()

```

```{r}
ggplot(pizza_data, aes(x = company, y = price_rupiah)) +
  geom_jitter(width = 0.2, alpha = 0.5, color = "darkgreen") +
  stat_summary(fun = mean, geom = "point", shape = 23, size = 3, fill = "red") +
  labs(title = "Pizza Prices by Company", x = "Company", y = "Price (Rp)") +
  theme_minimal()

```

### Feature engineering

price per inch

```{r}
pizza_data <- pizza_data %>%
  mutate(price_per_inch = price_rupiah / diameter)

```

yes/no columns to binary

```{r}
pizza_data <- pizza_data %>%
  mutate(
    extra_sauce_bin = ifelse(extra_sauce == "yes", 1, 0),
    extra_cheese_bin = ifelse(extra_cheese == "yes", 1, 0)
  )
```

one hot encoding

```{r}
library(fastDummies)
pizza_data <- fastDummies::dummy_cols(pizza_data, select_columns = c("variant", "company"))

```

### Building the models

starting with a basic model, predicting based on diameter

```{r}
model1 <- lm(price_rupiah ~ diameter, data = pizza_data)
summary(model1)

```

Predicting based on both diameter and size (small, med, large, etc.)

```{r}
pizza_data$size <- factor(pizza_data$size) # turn into factors
model2 <- lm(price_rupiah ~ diameter + size, data = pizza_data)
summary(model2)

```

### mixed models

comparing based on the different companies

```{r}
pizza_data$company <- factor(pizza_data$company) #set company to factor

mixed_model <- lmer(price_rupiah ~ diameter + extra_cheese_bin + extra_sauce_bin + 
                    (1 | company), data = pizza_data)

summary(mixed_model)

```

### Does diameter size change based on company

```{r}
mixed_model2 <- lmer(price_rupiah ~ diameter + extra_cheese_bin + extra_sauce_bin + 
                     (diameter | company), data = pizza_data)
summary(mixed_model2)
```

### Model Comparisons

```{r}
library(caret)
AIC(model1, model2, mixed_model, mixed_model2)

```
